---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
This is the repository for ZHENYI HUANG's HW07.

**NOTE: 
* This package is originally developed by @jennybc, please check here for the original GitHub repository [foofactor](https://github.com/jennybc/foofactors).
* This is a toy package created for expository purposes. It is not meant to actually be useful. If you want a package for factor handling, please see [forcats](https://cran.r-project.org/package=forcats).**

### foofactors

Factors are a very useful type of variable in R, but they can also drive you nuts. This package provides some helper functions for the care and feeding of factors.

### Installation

```{r installation, eval = FALSE}
devtools::install_github("STAT545-UBC-students/hw07-janehuang1647")
```
  
### Quick demo

Binding two factors via `fbind()`:

```{r}
library(foofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work. Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```

The `factor_check()` function returns a stopping message if the input is not a factor:
```{r}
factor_check(x)
```

The `freorder()`function returns a factor in a descending order:
```{r}
freorder(x)
```

The `fset_level()` function sets levels to the order in which they appear in the data, i.e. set the levels “as is”:
```{r}
y <- c("apple","coconut","banana")
yfx <- factor(y)
#check bothe the level of the original factor and after the fset_level() function.
levels(yfx) # the levels is ordered in alphabetical order
levels(fset_level(yfx))  # the level is ordered in the order of the original factor.
```

The `df_write()` write a dataframe into the file
```{r}
  df <- data.frame(
    testing = factor(c("a","b","c","a","c","e"), levels = c("a", "b","c","e"),
                     labels = c("A", "B","C","E")))


    df_write(df, "./test.csv", "./test.txt")
```
The `df_read()` then read the data from the file and retating the factor levels.

```{r}
df_read("./test.csv", "./test.txt")
```

