---
title: "stringsAsFactors = HELLNO"
author: "Zhenyi Huang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{stringsAsFactors = HELLNO}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Factors are a very useful type of variable in R, but they can also drive you nuts. Especially the "stealth factor" that you think of as character.

Can we soften some of their sharp edges?

Binding two factors via `fbind()`:

```{r}
library(foofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work.  Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```

The `freorder()`function returns a factor in a descending order. Let's see an exmaple from our previous homework:
```{r, original order,fig.width= 4,fig.height=2}
# first we load the gapminder first
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(tidyverse))

summary(gapminder)

# the original order for continent is alphabetical order.
gapminder %>% 
 select(lifeExp,continent) %>% 
  ggplot(aes(continent,lifeExp))+
  geom_boxplot(alpha=0.25, aes(fill=continent))
```
```{r, apply freorder() function, fig.width= 4, fig.height=2}
# now we apply the freorder() function to the continent, and we are expecting a reversed order.
gapminder %>% 
 select(lifeExp,continent) %>% 
  ggplot(aes(continent,lifeExp))+
  geom_boxplot(alpha=0.25, aes(fill=freorder(continent)))
```


The `fset_level()` function sets levels to the order in which they appear in the data, i.e. set the levels “as is”:
And again we use the same example, but compare it with the one applied with `fset_level()`.
```{r, original order 1, fig.width= 4,fig.height=2}

# the original order for continent is alphabetical order.
gapminder %>% 
 select(lifeExp,continent) %>% 
  ggplot(aes(continent,lifeExp))+
  geom_boxplot(alpha=0.25, aes(fill=continent))

  
```
```{r, apply fset_level(), fig.width= 4,fig.height=2 }
# now we apply the fset_level() function to the continent, and we are expecting an order which is the same as the entry appeared in the data frame.


gapminder %>% 
 select(lifeExp,continent) %>% 
  ggplot(aes(continent,lifeExp))+
  geom_boxplot(alpha=0.25, aes(fill=fset_level(continent)))

```


